\documentclass{resume} % Use the custom resume.cls style


\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 

\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Suryansh Jain} % Your name

% You can merge both of these into a single line if you do not have a website.

\address{+91 7574922552 \\ suryanshjain531@gmail.com} 

\address{\href{https://www.linkedin.com/in/suryanshjain31/}{LinkedIn} \\ \href{https://suryansh-jain-portfolio.netlify.app/}{Portfolio} \\ \href{https://github.com/iamsuryansh/}{GitHub} \\
}


\begin{document}


% ----------------------------------------------------------------------------------------

%     SUMMARY

% ----------------------------------------------------------------------------------------


\begin{rSection}{SUMMARY}


{Software Engineer with 4 years of experience building scalable \textbf{Python APIs} and backend systems within \textbf{microservice} architectures. Proficient in deploying applications using \textbf{Docker} and \textbf{Kubernetes}, developing with frameworks like \textbf{FastAPI} and Flask, and leveraging \textbf{AWS} for cloud infrastructure. Skilled in optimizing search with \textbf{Elasticsearch} and working in fast-paced \textbf{AGILE-SCRUM} environments.}


\end{rSection}


%----------------------------------------------------------------------------------------

%    WORK EXPERIENCE SECTION

%----------------------------------------------------------------------------------------


\begin{rSection}{EXPERIENCE}


\textbf{Samsung Research} \hfill Delhi, India

Software Engineer \hfill June 2022 - Present


 \begin{itemize}

    \itemsep -1pt {}


    \item Engineered a scalable backend using Python, Flask, and MySQL 
with advanced error handling and \textbf{Docker} CI/CD pipelines, reducing app 
certification time by 80\% for validating critical features in 250+ 
Tizen web apps.

    \item Architected secure backend APIs for 
authentication and real-time notifications using Flask and WebSockets, 
doubling QA team adoption from 4 to 8 by enabling seamless integration 
with a responsive ReactJS/TypeScript frontend.

    \item 
Optimized Q\&A ticket integration from Tizen Developers Portal using
 \textbf{Elasticsearch} with advanced querying and indexing strategies, 
accelerating data access and search efficiency by 50\% for seamless data
 retrieval in internal systems.

    \item Implemented a secure 
backend system for global Tizen App Store management with RBAC and 
session controls, enabling efficient application distribution and 
boosting app management efficiency by 75\% through enhanced reliability.


    \item Integrated key Tizen App Certification insights from a 45-day 
immersion at Samsung HQ in South Korea into backend systems and APIs, 
optimizing product roadmap decisions and enhancing alignment with Tizen 
TV QA teams.

    \item Engineered deeplink integrations for 
JioHotstar on Tizen and hosted app deployments for Tata Play, 
facilitating seamless partner enablement with 10+ collaborators (e.g., 
Disney+, HBO).

    \item Received Samsung Spot Award (2x) for impactful development and process optimization.


 \end{itemize}

 

\textbf{Standard Chartered Bank}\hfill Bangalore, India

Developer \hfill Aug 2021 - May 2022

 \begin{itemize}

    \itemsep -1pt {} 

    \item Developed Ethereum smart contracts for a blockchain-on-demand solution, boosting transaction throughput by 15\%.

    \item Developed Kafka-based error simulation pipeline for blockchain backend, increasing test coverage by 10\%.

     \item Optimized blockchain utilities with Python by creating a installable package, cutting development time by 20\%

    \item Secured "Best Project" at the Standard Chartered Developer Bootcamp (2021) among 12 competing teams.

 \end{itemize}


\end{rSection} 


%----------------------------------------------------------------------------------------

% TECHINICAL STRENGTHS    

%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}


\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex} \vspace{0.75ex}} l }

Programming & \textbf{Python}, JavaScript, SQL, Typescript, Java\\

Backend Frameworks & \textbf{FastAPI}, Flask, Django, Node.js\\

DevOps \& Cloud & \textbf{Docker}, \textbf{Kubernetes}, \textbf{AWS}, CI/CD, Git\\

Databases \& Search & MySQL, MongoDB, PostgreSQL, \textbf{Elasticsearch (SOLR concepts)}\\

Architecture & \textbf{Microservices}, RESTful APIs, System Design\\

Methodologies & \textbf{AGILE-SCRUM}, Cross-functional Collaboration\\

\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------

%    EDUCATION SECTION

%----------------------------------------------------------------------------------------


\begin{rSection}{Education}

{\bf Bachelor of Technology - VIT University, Vellore} \hfill {2017 - 2021}
\vspace*{5px}Electronics and Communication Engineering\hfill {GPA : 8.96}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex} \vspace{0.5ex}} l }

Value Added Program &  Introduction to Software Engineering\\

Publication & {Music Information Retrieval and Classification using Deep Learning \href{https://www.irjet.net/archives/V8/i6/IRJET-V8I6195.pdf}{(Publication)}}\\

Related Coursework & Data Structures and Algorithms, System Design, Object Oriented Programming,\\

& Database Management System, Computer Networks\\

 

\end{tabular}

%Member of Eta Kappa Nu \\

%Member of Upsilon Pi Epsilon \\

\end{rSection}


%----------------------------------------------------------------------------------------

%    PROJECT SECTION

%----------------------------------------------------------------------------------------




\end{document}

